### 2022-07-03 tex/sample_paper.tex
refactor code and restructure the directories
Update readme.md

Update readme.md

restructure

refactor code and restructure directories

some changes

some changes

trying to amke stuff work

still figuring it out

\usepackage{aistats2021}
% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\section{GENERAL FORMATTING INSTRUCTIONS}

The camera-ready versions of the accepted papers are 8 pages,
plus any additional pages needed for references.

Papers are in 2 columns with the overall line width of 6.75~inches (41~picas).
Each column is 3.25~inches wide (19.5~picas).  The space
between the columns is .25~inches wide (1.5~picas).  The left margin is 0.88~inches (5.28~picas).
Use 10~point type with a vertical spacing of
11~points. Please use US Letter size paper instead of A4.

Paper title is 16~point, caps/lc, bold, centered between 2~horizontal rules.
Top rule is 4~points thick and bottom rule is 1~point thick.
Allow 1/4~inch space above and below title to rules.

Author descriptions are center-justified, initial caps.  The lead
author is to be listed first (left-most), and the Co-authors are set
to follow.  If up to three authors, use a single row of author
descriptions, each one center-justified, and all set side by side;
with more authors or unusually long names or institutions, use more
rows.

Use one-half line space between paragraphs, with no indent.

\section{FIRST LEVEL HEADINGS}

First level headings are all caps, flush left, bold, and in point size
12. Use one line space before the first level heading and one-half line space
after the first level heading.

\subsection{Second Level Heading}

Second level headings are initial caps, flush left, bold, and in point
size 10. Use one line space before the second level heading and one-half line
space after the second level heading.

@@

\begin{thebibliography}{}
\setlength{\itemindent}{-\leftmargin}
\makeatletter\renewcommand{\@biblabel}[1]{}\makeatother
\bibitem{} J.~Alspector, B.~Gupta, and R.~B.~Allen (1989).
    \newblock Performance of a stochastic learning microchip.
    \newblock In D. S. Touretzky (ed.),
    \textit{Advances in Neural Information Processing Systems 1}, 748--760.
    San Mateo, Calif.: Morgan Kaufmann.

\bibitem{} F.~Rosenblatt (1962).
    \newblock \textit{Principles of Neurodynamics.}
    \newblock Washington, D.C.: Spartan Books.

\bibitem{} G.~Tesauro (1989).
    \newblock Neurogammon wins computer Olympiad.
    \newblock \textit{Neural Computation} \textbf{1}(3):321--323.
\end{thebibliography}

>>>>

\usepackage{aistats2021}
\usepackage{cite}

% If your paper is accepted, change the options for the package
% aistats2021 as follows:
%
%\usepackage[accepted]{aistats2021}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\section{Introduction}

Sampling algorithms play an important role in Statistics, in this case we refer to drawing samples from a probability density or distribution (not survey sampling). Monte Carlo Markov chain methods are commonly used for high dimensional sampling. In this paper, we look at Hamiltonian Monte Carlo, which uses hamiltonian dynamics to propose samples for the Metropolis algorithm. Bayesian Inference often uses parameters with constraints, but HMC optimizes on the unconstrained space. It is difficult to use Monte Carlo estimation on a constrained domain ~\cite{neal2008optimal}

\section{Transforms}

\subsection{Simplex Transforms}

\subsubsection{Softmax Transform}
The softmax function can be understood from Multinomial Logistic Regression employed for predicting probabilities of a Categorically distributed variable. Geometrically it maps $R^K$ to the boundary of a unit K-simplex(it is simply the convex hull of $k+1$ affinely independent points in $R^K$. Essentially it transforms a vector of size K to another vector of size K where the outputs sum to 1. It is worth noting that the mapping is actually from $R^K$ to $R^{K-1}$, so when a vector of size $K$ is transformed the $K_th$ vector is simply $1$- sumofk-1 vectors

@@

\bibliography{mybib}{}
\bibliographystyle{plain}
